\documentclass[12pt]{article}  % 12 points is a good size, but you can use 11
\usepackage{fullpage}          % more lines and longer lines per page
\usepackage[style=numeric]{bibtex}
\addbibresource{s.bib}
\begin{document}
\title{AI Ethical Issue}
\author{Amber Wong}
\maketitle                     % generates the title
\section{Introduction}
The continuous development and widespread application of artificial intelligence have brought great benefits to society. The areas of image recognition, speech recognition, and autonomous driving have all improved the convenience of life to a certain extent. However, the moral crisis behind artificial intelligence makes a large number of people skeptical about it. The privacy of data and the personal information of images and citizens without legal and ethical constraints will greatly threaten the security of society. \newline\newline
Many people worry that machine learning is faster and faster than humans.Will it be ruled by machines when artificial intelligence develops to the late stage? However, the machine only learns according to the instructions of the code, and the engineer who writes the code of the machine learning is the real decision maker. Therefore, we should pay more attention to moral issues in the development of artificial intelligence, including AI bias, privacy concerns, and unemployment caused by artificial intelligence. By paying attention to the development of artificial intelligence, we ensure that artificial intelligence is truly beneficial to human society.
\section{Background}
Human beings are not born with knowledge, but by constantly learning by summing up experiences from behaviors,  summing up right and wrong from a lot of exercises, and then master a certain skill. In recent years, scientists have discovered that computers can also simulate or implement human learning behaviors to acquire new knowledge or skills. \newline\newline
This kind of technical science that simulates, extends and expands human intelligence theory, method, technology and application system is artificial intelligence. Artificial intelligence is a branch of computer science.It attempts to understand the essence of intelligence and produce a new kind of intelligent machine that can respond in a similar way to human intelligence. Natural language processing, etc.
\section{Main Body}
	The development of artificial intelligence certainly needs to be closely followed, especially its AI bias, AI privacy concerns, and unemployment caused by artificial intelligence.
\subsection{Specific Advances: AI Bias}
	Google's photo service shows that artificial intelligence is used to identify people, objects and scenes. But this can go wrong. For example, when the camera did not write down race-sensitive markers, some image recognition software had previously mistakenly labeled black people as "chimps" or "apes." Deep learning is a typical "black box" algorithm. Even the designer may not know how the algorithm makes decisions. It is technically difficult to find out whether there are discriminations and root causes in the system.
\subsection{Specific Advances: Privacy Concerns}
	The current society is an Internet age, and anyone ’s private information and daily life schedules will leak through the Internet. If the privacy data of artificial intelligence is not encrypted, it may cause social risks. However, in the article "How Can AI Systems Understand Human Values?", If a patient goes for a private psychological consultation, the preference level will be renewed and a more accurate judgment will be made after being understood by the machine. Because agent-based artificial intelligence only knows about choices, it doesn't know the reasons behind them. Therefore, it is necessary to consider whether privacy should be provided to artificial intelligence.
\subsection{Specific Advances: Unemployment Caused By Artificial Intelligence}
	Artificial intelligence can replace most repetitive manual labor and even auto-driving trucks. In the era when artificial intelligence is highly popular in the future, how will social governments deal with these unemployed people? The popularity of machines will maximize the productivity of society. Whether or not to replace manpower with artificial intelligence is one of the issues that the government needs to consider.
	Consider from the three aspects of government, industry and scholars.
\subsection{Steps: Government}
	The government should supervise algorithms, including design standards, responsibility standards, code transparency, and algorithm decision transparency. In addition, there is an approval system that cannot be launched to the market without approval.
\subsection{Steps: AI developers}
	AI developers need to adhere to some basic ethical guidelines, including general guidelines for research and development, transparency guidelines, and value guidelines. Programmers should write the laws and morals of human society into AI systems.
\subsection{Steps: Scholars}
	Scholars should strive to study how to build a complete value learning system. The sole goal of making robots is to maximize the realization of human value. And we can consider humans, that is, human behavior provides information about human value, and robots need to be able to consider and weigh our value on their own.
\section{Conclusions}
	As AI is increasingly used in life, we can consider modifying and improving some of the current social constraints. Connect related interdisciplinary subjects, collaborate and study AI-related ethics. But if we worry too much about artificial intelligence, it will hinder the actual progress of artificial intelligence. Combining ethical considerations, artificial intelligence really benefits the public.
\printbibliography
\end{document}








\bibliography{mybibliofile}
